Arhangelskii's \(\alpha\)-principles and selection games

### 2020-05-20 articles/selection-alpha-games/article.tex
prepare for arxiv
remove line numbers for arxiv
dedicate paper to Zenor for submission

Noting that \(\plI\win G_1(\Gamma_X,\Gamma_X)\) if and only if
\(\plI\win G_{fin}(\Gamma_X,\Gamma_X)\) \cite{MR2417134}, but
the same is not true of \(G_\star(\Gamma_{X,x},\Gamma_{X,x})\)
(i.e. there are \(\alpha_4\) spaces that are not \(\alpha_2\)
\cite{shakhmatov2002convergence}),
we also ask the following.

@@

\section{Acknowledgements}

@@

\bibliographystyle{plain}
\bibliography{../../bibliography}

>>>>

Noting that \(\plI\win G_1(\Gamma_X,\Gamma_X)\) if and only if
\(\plI\win G_{fin}(\Gamma_X,\Gamma_X)\) \cite{MR2417134}, but
the same is not true of \(G_\star(\Gamma_{X,x},\Gamma_{X,x})\)
(e.g. there are \(\alpha_4\) spaces that are not \(\alpha_2\)
\cite{shakhmatov2002convergence}),
we also ask the following.

@@

\section{Acknowledgements and Dedication}

@@

This paper is dedicated to the memory of Dr. Phil Zenor. Dr. Zenor
was the instructor of the author's undergraduate real analysis course,
which was taught using inquiry-based learning.
The author was first inspired to become a mathematician because
Dr. Zenor's class modeled the experience of being a mathematician;
rather than listening to lectures, students in Dr. Zenor's class
were encouraged and rewarded for engaging with the material
themselves and presenting their findings to their peers.

\bibliographystyle{plain}
\bibliography{bibliography}
